---
title: "HOW TO USE SETS IN R"
author: "Erasto Oraro"
date: "7-02-2021"
output: pdf_document
---
***
# Data Structures - Set

Sets define a ‘collection’ of objects, or things typically referred to as ‘elements’ or ‘members.’ The concept of sets arises naturally when dealing with any collection of objects, whether it be a group of numbers or anything else. Conceptually, the following examples can be defined as a ‘set’:

* {1, 2, 3, 4} 
* {Red, Green, Blue} 
* {Cat, Dog} 

## Set Operations
Declare sets
```{r}
x <- c(1,2,5,13,6)
x
```
```{r}
y <- c(5,1,8,9,10,13,20)
y
```

R includes some handy set operations, including these:

1. union(x,y):- Union of the sets x and y -> ($x\cup y$).
  
2. intersect(x,y):- Intersection of the sets x and y -> ($x\cap y$).

3. setdiff(x,y):- Set difference between x and y, consisting of all elements of x that are not in y -> ($x\setminus y$).

4. setequal(x,y):- Test for equality between x and y

5. c %in% y:- Membership, testing whether c is an element of the set y

6. choose(n,k):- Number of possible subsets of size k chosen from a set of size n

\newpage
**Examples:**

```{r}

union(x,y)

intersect(x,y)

setdiff(x,y)

setdiff(y,x)

setequal(x,y)

setequal(x,c(1,2,5))

2 %in% x

2 %in% y

choose(5,2)

```